Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-14 paper.tex
Cite METS paper earlier
Cite METS wake stuff earlier too

Blackwell et al. investigated the effects of Reynolds number on the performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed significant
Reynolds number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$ \cite{Bravo2007}.

The wake of a cross-flow turbine in the dynamic stall regime has been studied
via laser Doppler velocimetry by Brochier et al. \cite{Brochier1986} and with
particle image velocimetry (PIV) by Fujisawa and Shibuya \cite{Fujisawa2001}.
However, both of these studies were performed at very low Reynolds
numbers---$Re_D = 10^4$ and $10^3$, respectively. Tescione et al.
\cite{Tescione2014} studied the wake of a vertical-axis wind turbine in a wind
tunnel using stereo PIV at an approximate blade chord Reynolds number $Re_c =
1.7 \times 10^5$; very close to the $Re$-independent state reported in
\cite{Bachant2014}.

>>>>

Blackwell et al. investigated the effects of Reynolds number on the performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed significant
Reynolds number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$ \cite{Bravo2007}. Bachant and Wosnik \cite{Bachant2014} observed
Reynolds number independence of power coefficient at optimal tip speed ratio for
a high solidity cross-flow turbine at $Re_D \approx 10^6$ or
$Re_{c,\mathrm{avg}} \approx 2 \times 10^5$.

The wake of a cross-flow turbine in the dynamic stall regime has been studied
via laser Doppler velocimetry by Brochier et al. \cite{Brochier1986} and with
particle image velocimetry (PIV) by Fujisawa and Shibuya \cite{Fujisawa2001}.
However, both of these studies were performed at very low Reynolds
numbers---$Re_D = 10^4$ and $10^3$, respectively. Tescione et al.
\cite{Tescione2014} studied the wake of a vertical-axis wind turbine in a wind
tunnel using stereo PIV at an approximate blade chord Reynolds number $Re_c =
1.7 \times 10^5$; very close to the $Re$-independent state reported in
\cite{Bachant2014}, where 2-D near-wake profiles were measured for a high
solidity cross-flow turbine at optimal tip speed ratio.
